---
title: "Eating Out"
author: "Ruben Murillo Villa"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Methods

Response variable is categorical: Dine out lat week? Yes or No

Explanatory variable is race, it too, is a categorical variable
So we use cat~cat 

Inference: chi=squared and fisher exact tests

# Descriptive Summaries

## Graphical Descriptive Summary

### Bar Chart

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

White tend to be the outlier in this bar plot. Since their percent of dining out is the highest (close to 85% of white people dine out according to this bar plot). Black and other are relatively the same with "other" only being a slightly higher. 

## Numcerical Descriptive Summary

```{r}
table1 <- xtabs(~~race + eatout,data=mydata)
rowPerc(table1)
colPerc(table1)
```

Based off of the data table on top, more white dine out compared to the other (black & other). White's dine out more by 14.07 compared to black people. White's dine out more by 10.99 compared to other people. This data table only further proves that there is a difference between the 3 options. White dines out more. 

## Inferential Results


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The p-value is 0.000002287. The p-value is too small so we have to reject the null hypothesis. There is a difference between race and how frequent they dine out. That's what the chi squared test gave us.

## Fisher

```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```

The p-value is less then 0.05 therefore we fail to reject.

# Conclusion

Both tests have a p value of less then 0.05 and therefore we fail to reject the null hypothesis. White people are more likely to eat out then black people or other. 